Human Factors Influencing Visual Statistical Inference

### 2014-01-09 sociology_paper.tex
references updated

% Article top matter
\title{Human Factors Influencing Visual Statistical Inference }
\author{{Mahbubul Majumder, Heike Hofmann, Dianne Cook}
\thanks{Mahbubul Majumder is an Assistant Professor in the Department of Mathematics, University of Nebraska at Omaha (e-mail: mmajumder@unomaha.edu), Heike Hofmann and Dianne Cook are Professors in the Department of Statistics and Statistical Laboratory, Iowa State University, Ames, IA 50011-1210. This research is supported in part by the National Science Foundation Grant \# DMS 1007697.}}
\date{\vspace{-.5in}}
%\date{\today}  %\today is replaced with the current date
\maketitle

>>>>

% Article top matter
\title{Human Factors Influencing Visual Statistical Inference }
\author{{Mahbubul Majumder, Heike Hofmann, Dianne Cook}
\thanks{Mahbubul Majumder is an Assistant Professor in the Department of Mathematics, University of Nebraska at Omaha, NE 68182 (e-mail: mmajumder@unomaha.edu), Heike Hofmann and Dianne Cook are Professors in the Department of Statistics and Statistical Laboratory, Iowa State University, Ames, IA 50011-1210. This research is supported in part by the National Science Foundation Grant \# DMS 1007697.}}
\date{\vspace{-.5in}}
%\date{\today}  %\today is replaced with the current date
\maketitle
